---
output:
  html_document:
    df_print: default
    keep_md: yes
  pdf_document: 
    keep_tex: yes
---
```{r, echo=FALSE}
my_render <- function(Project2.Rmd, encoding) {
    rmarkdown::render(Project2.Rmd, clean = FALSE, encoding = encoding)
}
```
---
title: "Developing Data Products Week 2 Assignment"
author: "Girish Desai"
date: "June 17, 2018"
output: html_fragment
---

# Instructions

Create a web page using R Markdown that features a map created with Leaflet.

Host your webpage on either GitHub Pages, RPubs, or NeoCities.

Your webpage must contain the date that you created the document, and it must contain a map created with Leaflet. We would love to see you show off your creativity!

# Criteria

The rubric contains the following two questions:

- Does the web page feature a date and is this date less than two months before the date that you're grading this assignment?
- Does the web page feature an interactive map that appears to have been created with Leaflet?


## Print the map

```{r}
library(knitr)
library(leaflet)
suppressPackageStartupMessages(library(dplyr))

Map <- leaflet() %>%
  addTiles() %>%  # Add default OpenStreetMap map tiles
  addMarkers(lat=40.712772, lng=-74.006058, popup="New York City Hall") %>%
  addMarkers(lat=40.785091,lng=-73.968285, popup="Central Park, New York") %>%
  addMarkers(lat=40.748817,lng=-73.985428	, popup="Empire State Building") %>%
  addMarkers(lat=40.750580,lng=-73.993584, popup="Penn Station, New York") 
 
Map  
```


# Mapping Clusters

When you zoom in to each cluster, the cluster will seperate until you see the individual Markers.

```{r}
df <- data.frame(lat=runif(500, min=40.712772, max = 40.785091 ),
                 lng=runif(500, min=-74.006058, max = -73.968285))
df %>%
leaflet() %>%
addTiles() %>%  
addMarkers(clusterOptions = markerClusterOptions())  
```



